An Improved Method for Coupling Hydrodynamics with Reaction Networks and Nuclear Statistical Equilibrium

### 2021-04-29 simplified_sdc_intro/paper.tex
update table
some discussion on interface states

@@

\begin{deluxetable}{lllllll}
\tablecaption{\label{table:nse_strang_methodII} Convergence ($L_1$ norm) for the NSE convergence
problem using the simplified-SDC algorithm.}
\tablehead{\colhead{field} & \colhead{$\epsilon_{64 \rightarrow 128}$} & 
           \colhead{rate} & \colhead{$\epsilon_{128\rightarrow 256}$} & 
           \colhead{rate} & \colhead{$\epsilon_{256\rightarrow 512}$}}
\startdata
 $\rho$                      & $4.558 \times 10^{19}$  & 1.633  & $1.470 \times 10^{19}$  & 1.578  & $4.923 \times 10^{18}$  \\
 $\rho u$                    & $1.945 \times 10^{28}$  & 1.648  & $6.208 \times 10^{27}$  & 1.513  & $2.176 \times 10^{27}$  \\
 $\rho v$                    & $1.945 \times 10^{28}$  & 1.648  & $6.208 \times 10^{27}$  & 1.513  & $2.176 \times 10^{27}$  \\
 $\rho E$                    & $5.710 \times 10^{37}$  & 1.620  & $1.857 \times 10^{37}$  & 1.552  & $6.333 \times 10^{36}$  \\
 $\rho e$                    & $5.708 \times 10^{37}$  & 1.620  & $1.857 \times 10^{37}$  & 1.553  & $6.331 \times 10^{36}$  \\
 $T$                         & $5.873 \times 10^{20}$  & 1.621  & $1.910 \times 10^{20}$  & 1.494  & $6.779 \times 10^{19}$  \\
 $\rho X(\isotm{H}{1})$      & $4.558 \times 10^{-11}$ & 1.633  & $1.470 \times 10^{-11}$ & 1.578  & $4.923 \times 10^{-12}$ \\
 $\rho X(\isotm{He}{4})$     & $2.453 \times 10^{17}$  & 1.835  & $6.876 \times 10^{16}$  & 1.657  & $2.181 \times 10^{16}$  \\
 $\rho X(\isotm{C}{12})$     & $1.130 \times 10^{12}$  & 1.846  & $3.145 \times 10^{11}$  & 1.678  & $9.831 \times 10^{10}$  \\
 $\rho X(\isotm{O}{16})$     & $5.339 \times 10^{12}$  & 1.830  & $1.502 \times 10^{12}$  & 1.667  & $4.730 \times 10^{11}$  \\
 $\rho X(\isotm{Cr}{48})$    & $6.880 \times 10^{18}$  & 1.791  & $1.988 \times 10^{18}$  & 1.601  & $6.554 \times 10^{17}$  \\
 $\rho X(\isotm{Fe}{52})$    & $3.470 \times 10^{19}$  & 1.606  & $1.140 \times 10^{19}$  & 1.608  & $3.740 \times 10^{18}$  \\
 $\rho X(\isotm{Fe}{54})$    & $4.766 \times 10^{20}$  & 1.764  & $1.403 \times 10^{20}$  & 1.777  & $4.093 \times 10^{19}$  \\
 $\rho X(\isotm{Ni}{56})$    & $4.835 \times 10^{20}$  & 1.781  & $1.407 \times 10^{20}$  & 1.788  & $4.075 \times 10^{19}$  \\
 $\rho Y_e$                  & $2.370 \times 10^{19}$  & 1.644  & $7.582 \times 10^{18}$  & 1.580  & $2.536 \times 10^{18}$  \\
 $\rho \bar{A}$              & $4.061 \times 10^{21}$  & 1.678  & $1.270 \times 10^{21}$  & 1.675  & $3.975 \times 10^{20}$  \\
 $\rho (B/A)$                & $4.224 \times 10^{20}$  & 1.664  & $1.333 \times 10^{20}$  & 1.602  & $4.391 \times 10^{19}$  \\
\enddata
\end{deluxetable}

>>>>

      In the unsplit CTU method \citep{ppmunsplit}, the interface
      states used for the final Riemann problem through the zone
      interface consist of a normal predictor and a transverse flux
      correction.  We can add the source terms either to the normal
      predictor (for example, doing characteristic tracing as
      described in \citealt{ppm}) or after all of the transverse flux
      corrections are made.  Both are second-order accurate.  For the
      hydrodynamics sources, we do those in the normal predictor.
      However, for the reactive sources, we found that it is most
      reliable to add them at the end of the interface state
      construction, after the transverse flux corrections.  This is
      because we want to ensure that sum over species of $\Ic_\qb$ is
      zero, and characteristic tracing or the various flux corrections
      may not preserve this.

@@

\begin{deluxetable}{lllllll}
\tablecaption{\label{table:nse_strang_methodII} Convergence ($L_1$ norm) for the NSE convergence
problem using the simplified-SDC algorithm.}
\tablehead{\colhead{field} & \colhead{$\epsilon_{64 \rightarrow 128}$} & 
           \colhead{rate} & \colhead{$\epsilon_{128\rightarrow 256}$} & 
           \colhead{rate} & \colhead{$\epsilon_{256\rightarrow 512}$}}
\startdata
 $\rho$                      & $4.553 \times 10^{19}$  & 1.636  & $1.465 \times 10^{19}$  & 1.583  & $4.891 \times 10^{18}$  \\
 $\rho u$                    & $1.949 \times 10^{28}$  & 1.650  & $6.210 \times 10^{27}$  & 1.513  & $2.176 \times 10^{27}$  \\
 $\rho v$                    & $1.949 \times 10^{28}$  & 1.650  & $6.210 \times 10^{27}$  & 1.513  & $2.176 \times 10^{27}$  \\
 $\rho E$                    & $5.691 \times 10^{37}$  & 1.622  & $1.848 \times 10^{37}$  & 1.561  & $6.266 \times 10^{36}$  \\
 $\rho e$                    & $5.689 \times 10^{37}$  & 1.622  & $1.848 \times 10^{37}$  & 1.561  & $6.265 \times 10^{36}$  \\
 $T$                         & $5.778 \times 10^{20}$  & 1.740  & $1.729 \times 10^{20}$  & 1.702  & $5.316 \times 10^{19}$  \\
 $\rho X(\isotm{H}{1})$      & $4.553 \times 10^{-11}$ & 1.636  & $1.465 \times 10^{-11}$ & 1.583  & $4.891 \times 10^{-12}$ \\
 $\rho X(\isotm{He}{4})$     & $2.541 \times 10^{17}$  & 1.807  & $7.262 \times 10^{16}$  & 1.634  & $2.339 \times 10^{16}$  \\
 $\rho X(\isotm{C}{12})$     & $1.140 \times 10^{12}$  & 1.838  & $3.189 \times 10^{11}$  & 1.670  & $1.002 \times 10^{11}$  \\
 $\rho X(\isotm{O}{16})$     & $5.413 \times 10^{12}$  & 1.819  & $1.535 \times 10^{12}$  & 1.658  & $4.864 \times 10^{11}$  \\
 $\rho X(\isotm{Cr}{48})$    & $7.020 \times 10^{18}$  & 1.793  & $2.026 \times 10^{18}$  & 1.614  & $6.621 \times 10^{17}$  \\
 $\rho X(\isotm{Fe}{52})$    & $3.631 \times 10^{19}$  & 1.579  & $1.215 \times 10^{19}$  & 1.597  & $4.018 \times 10^{18}$  \\
 $\rho X(\isotm{Fe}{54})$    & $4.670 \times 10^{20}$  & 1.807  & $1.335 \times 10^{20}$  & 1.869  & $3.654 \times 10^{19}$  \\
 $\rho X(\isotm{Ni}{56})$    & $4.858 \times 10^{20}$  & 1.808  & $1.387 \times 10^{20}$  & 1.860  & $3.820 \times 10^{19}$  \\
 $\rho Y_e$                  & $2.372 \times 10^{19}$  & 1.649  & $7.564 \times 10^{18}$  & 1.587  & $2.518 \times 10^{18}$  \\
 $\rho \bar{A}$              & $4.009 \times 10^{21}$  & 1.693  & $1.240 \times 10^{21}$  & 1.690  & $3.843 \times 10^{20}$  \\
 $\rho (B/A)$                & $4.222 \times 10^{20}$  & 1.666  & $1.330 \times 10^{20}$  & 1.605  & $4.374 \times 10^{19}$  \\
\enddata
\end{deluxetable}
